---
title: "covid 19"
author: "Christina Maayah"
date: "DECEMBER 3 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

$H_0$:no difference between death rate due to covid 19 betwen men and women   

$H_1$: there is a difference betwen rate due to covid 19 between men and women

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex

## We create two bar charts - one based on frequency and the other on percent


```{r}
barchartGC(~result + sex,data=kRdata)
barchartGC(~result + sex,data=kRdata, type="percent")

```
  
the bar chart shows that more males than femals had daied from covid 19 
 
Table of patients:
```{r}
table1 <- xtabs(~result + sex,data=kRdata)
rowPerc(table1)
colPerc(table1)
print(table1)
```
  
the numerical summury shows the larger pricentage of males died than the females 
  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
  
the oods of diiying if youre  a male 2.3 times grater then if your a female   
95 percent confidence interval is 1.4 to  3.9 . this means that the oods of men diying are significantly grater than the females   
  
## Conclusions
  
diying is not independent of sex , men are most likely to die than womens 
